---
title: "Using Weather and Ice Cream Tools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using Weather and Ice Cream Tools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Using Weather and Ice Cream Tools

This tutorial demonstrates how to use the `bpartyRonyLittle` package for weather forecasting and simulating ice cream consumption. The package combines weather data and simulation tools to estimate ice cream volume for fun and practical use cases.

---

## Installation

First, install the package from GitHub using the `devtools` package:

```{r}
# Install the package
devtools::install_github("ptds2024/bpartyRonyLittle")
```

Load the package:
```{r}
library(bpartyRonyLittle)
```

## Fetching Weather Data

The bpartyRonyLittle package retrieves weather data using the OpenWeatherMap API.

## Check City Validity

You can verify if a city is available in the API database using the check_city_validity function:
```{r}
# Check if Lausanne is a valid city
api_key <- "388c46f24ed4124776271a0d7e62bbb1"
is_valid <- check_city_validity("Lausanne", api_key = api_key)
print(is_valid)
```

## Fetch a 5-Day Weather Forecast
Use the get_forecast function to get detailed weather information for the next 5 days:

```{r}
# Fetch weather data for Lausanne
forecast <- get_forecast("Lausanne", api_key = api_key)
head(forecast)
```

## Simulating Cone Volume

The package includes functions to calculate the radius of an ice cream cone over time and simulate its changes.

## Calculate Cone Radius

The cone_radius function computes the radius of a cone based on the given input x:

```{r}
# Calculate the radius for a single time point
radius <- cone_radius(5)
print(radius)

# Calculate the radius for a sequence of time points
radii <- cone_radius_for(1:10)
print(radii)
```

## Plotting Cone Radius

You can visualize how the cone's radius changes over time:

```{r}
# Plot cone radius over time
radii <- cone_radius_for(1:20)
plot(1:20, radii, type = "b", col = "blue", pch = 19,
     main = "Cone Radius Over Time",
     xlab = "Time", ylab = "Radius",
     sub = "This plot shows how cone radius changes over time")
```

## Using the Shiny App

The package includes a Shiny app for interactive weather and ice cream analysis. Use the run_app function to launch the app:

```{r}
# Launch the Shiny app
run_app(api_key = api_key)
```

## Example Workflow
Here’s a complete example workflow that combines weather data retrieval and cone volume simulation:

```{r}
# Step 1: Verify the city
is_valid <- check_city_validity("Lausanne", api_key = api_key)
if (!is_valid) stop("City not found!")

# Step 2: Fetch weather data
forecast <- get_forecast("Lausanne", api_key = api_key)

# Step 3: Simulate cone radius over 10 time points
radii <- cone_radius_for(1:10)

# Step 4: Plot results
plot(1:10, radii, type = "b", col = "darkgreen", pch = 16,
     main = "Simulated Cone Radius Over Time",
     xlab = "Time", ylab = "Radius",
     sub = "This plot shows the simulated cone radius over 10 time points.")
```

## Summary

This tutorial demonstrated how to:

- Fetch weather data using the OpenWeatherMap API.
- Simulate and visualize ice cream cone volume over time.
- Use the Shiny app for interactive analysis.
